Understanding and Verifying the Shape of Stencil Computations

### 2017-03-27 oopsla17/lattice-model.tex
Consistency checking

\subsection{Consisteny}

>>>>

\subsection{Consistency}

Once the specification is synthesised into objects in the model and stencil
under examination is analysed, consistency checking itself is remarkably simple.
Two stage checking is outlined below.

\begin{enumerate}
  \item Multiplicity of the model is checked against the stencil. The only way
    this fails is if the original specification involved \texttt{readOnce}, but
    some indexing occur multiple times in the stencil.  Note that absence of
    \texttt{readOnce} is interpreted liberally, and if the stencil indices
    happen to occur uniquely, this does not constitute a failure.
  \item Definition of vector intervals is completely unwinded into sets of
    offset tuples and depending the approximation modifier (or lack thereof)
    we compare these tuples to offsets of the stencil computation. Lower and
    upper bounds are checked with subset and superset relations respectively,
    while absence of \texttt{atMost} and \texttt{atLeast} results in exact
    checking with set equality.
\end{enumerate}

Here is the mathematical definition of consistency checking:
\begin{align*}
  \textit{consistent}(\textit{ix}, \textit{model}) & = \begin{cases}
    \textsf{false} & \textit{model} = \textsf{once}(x) \wedge ix = \textsf{mult}(y) \\
    \textit{consistent'}(\textit{peel}(ix), \textit{peel}(model)) & \textit{otherwise}
  \end{cases} \\
%
  \textit{consistent'}(\textit{ix}, \textit{model}) & = \begin{cases}
    m = ix & \textit{model} = \textsf{exact}(m) \\
    m \supseteq ix & \textit{model} = \textsf{upper}(m) \\
    m \subseteq ix & \textit{model} = \textsf{lower}(m)
  \end{cases}
\end{align*}
